Example penalized LTRC survival model with simulated data

### 2021-07-28 example.Rmd
Add link to paper in example.Rmd

# Introduction
This guide shows how to use penalized survival models for prediction with left-truncated and right-censored data (LTRC) as described in McGough *et al.* 2021. The analyses utilize a simulated dataset based on the Foundation Medicine and Flatiron Health Clinico-Genomic Database (CGDB), as described in the paper.

>>>>

# Introduction
This guide shows how to use penalized survival models for prediction with left-truncated and right-censored data (LTRC) as described in [McGough *et al.* 2021](https://onlinelibrary.wiley.com/doi/10.1002/sim.9136). The analyses utilize a simulated dataset based on the Foundation Medicine and Flatiron Health Clinico-Genomic Database (CGDB), as described in the paper.
